Alessandroni-2022

### 2024-10-23 doc/charting/Alessandroni-2022.qmd
update data extraction from my studies
Update Alessandroni-2022.qmd
Added a couple of barriers I found relevant. Other than that, this paper is all over the place and it has less workflow or structure than otherrs. Interesting, but does not add anything new if you have read the others.

@@

-   Markdown/quarto - collaborative writing - all
-   Github - version control - all

@@

-   Incorporating open tools may have a steep learning curve
-   Open science in the curricula vitae of academics must become a
    requirement and not just a nice addition
-   The problem with current incentive structures such as impact factor

>>>>

## Characteristics of the paper

-   Type of paper (e.g., tips, example): guide
-   Themes (e.g., tools, organization): organization, tools
-   Other keywords (e.g., newcomers):

@@

-   Markdown/quarto - collaborative writing - all
-   Github/Gitlab - version control - all

@@

-   Incorporating open tools may have a steep learning curve
-   Concerns about data safety
-   High prices for making papers open
-   Open science in the curricula vitae of academics must become a
    requirement and not just a nice addition
-   The problem with current incentive structures such as impact factor
